---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `brfss2013`. Delete this note when before you submit 
your work. 

```{r load-data}
load("brfss2013.RData")
```



* * *

## Part 1: Data
I am trying to build a relation between  women and their health condition considering their pregency.
here I am creating a new varriable with mutate goodhealth, fair and poor is considered as not good health.
I am also creating a per varriable wh
```{r}
WomenHealthData = brfss2013 %>% 
  select(pregnant,hlthpln1,genhlth,sex,exerany2,marital) %>%
  filter(sex=='Female',marital=='Married',!is.na(pregnant), !is.na(hlthpln1), !is.na(genhlth),!is.na(sex),!is.na(exerany2)) %>%
  mutate(goodhealth=as.factor(ifelse(genhlth=="Excellent" | genhlth=="Very good" | genhlth=="Good" ,"Yes","No")))

WomenHealthData$goodhealth =factor(WomenHealthData$goodhealth , levels = c("Yes", "No"))

CleanWomenHealthData = WomenHealthData %>%
  select(pregnant,hlthpln1,exerany2,goodhealth)
```



* * *

## Part 2: Research questions

**Research quesion 1:**
Healthier women are getting more pregnants then women with poor health condition? -> their percentage is more

**Research quesion 2:**
Women heving healthcare coverage are more healthier then those does not have healthcare coverage?

**Research quesion 3:**
Pregnant women those who excrise having good health condition?
* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

**Research quesion 1:**

```{r}
 CleanWomenHealthData %>%
  group_by(goodhealth,pregnant) %>%
  summarise(count=n()) %>%
   mutate(per=paste0(round(100*count/sum(count),2),'%'))
```

```{r}

ggplot(CleanWomenHealthData,aes(x=goodhealth, fill=pregnant))  + geom_bar()
```



**Research quesion 2:**

```{r}
CleanWomenHealthData %>%
  group_by(goodhealth,hlthpln1) %>%
  summarise(count=n()) %>%
   mutate(per=paste0(round(100*count/sum(count),2),'%'))
```

```{r}
ggplot(CleanWomenHealthData,aes(x=goodhealth, fill=hlthpln1))  + geom_bar()
```



**Research quesion 3:**

```{r}
 CleanWomenHealthData %>%
  filter(pregnant == "Yes") %>%
  group_by(goodhealth,exerany2) %>%
  summarise(count=n()) %>%
   mutate(per=paste0(round(100*count/sum(count),2),'%'))
```

``` {r}
ggplot(CleanWomenHealthData,aes(x=goodhealth, fill=exerany2))  + geom_bar()
```
